\section{List of Requirements} \label{sec:lor}

The following listed content is to be considered relevant to implement in order to answer to the final problem statement. The following list will be denoted into a bulletin order, in no particular order.

\subsubsection{Video game requirements}

\begin{itemize}
\item The video game utilized should be an variation of Pacman.
\item The incorporated AI must be a finite state machine.
\item The ghost modes must represent the states in the finite state machine.
\item the modes must be of type; Chase, Scatter and Frightened mode. (See section XX -2,2)
\end{itemize}


The following requirements are a list of features that must be implemented in the game.

\begin{itemize}
\item The game area must be a maze, similar to the original Pacman.(See section XX)
\item The game should have a playing agent similar to the original Pacman.(See section XX)
\item the game must include dots and energizers similar to the original Pacman.(See section XX)
\item the game must include an AI pathfinding system similar to the original Pacman.(See section XX)
\end{itemize}


\subsubsection{Genetic Algorithm}
The following content is considered to be required to construct, develop and implement a functional genetic algorithm in accordance with the final problem statement.


\begin{itemize}
\item Problem definition.(The GA is utilized to find one or some set of solutions to a given problem.)
\item Population size.
\item Chromosomes.(gene encoding)
\item Fitness function and Fitness Score representation
\item Selection method operator
\item Crossover operator function and crossover probability
\item Mutation operator function and mutation probability
\item result representation
\item algorithm termination
\end{itemize}


